### 2011-01-26 paper/platformDetails.tex
added sentence about the wireless ethernet
Made wii/LEd light photos smaller, put them together.

The quadruped robot has an on-board computer running Linux. The lower
level drivers are in C and the system is implemented in
Python.

\acmFig{robot.JPG}{1}{The infrared LED mounted on top of the robot, which
provides feedback about distance traveled in conjunction with a Wii
remote}
\acmFig{wiiMote.JPG}{1}{A Wii remote tracks the location of the robot,
providing feedback about distance traveled}

A Nintendo Wii remote tracks the location of the robot, providing feedback
about distance traveled, in pixels, through an infrared LED mounted on top of 
the robot. A server is run on the robot and continuously tracks its
position using the CWiid library\cite{cwiid} to interface with the remote
via bluetooth. A client then connects via a socket to the tracking
server and requests position updates periodically. If the robot walks 
beyond the viewable range of the Wii remote, a prompt informed the
user. The only human intervention required during the
experiment was to move the robot back inside the viewable area and resume
the run, and to handle any mechnanical failures that arose. This did not
interrupt the learning process or result in the loss of data.

>>>>

The quadruped robot (\figref{robot_close.jpg}) has an on-board computer running Linux. The lower
level drivers are in C and the system is implemented in
Python.

\acmFigg{wiiMote.JPG}{robot.JPG}{1}{A Nintendo Wii remote tracks the location
of the robot, providing feedback about distance traveled, in pixels, through
an infrared LED mounted on top of the robot.}

We controlled the experiments from a computer that was connected via a
wireless Ethernet to the robot. A Nintendo Wii remote tracks the location 
of the robot, providing feedback
about distance traveled, in pixels, through an infrared LED mounted on top of 
the robot (\figref{wiiMote.JPG}). A server is run on the robot and continuously tracks its
position using the CWiid library\cite{cwiid} to interface with the remote
via bluetooth. A client then connects via a socket to the tracking
server and requests position updates periodically. If the robot walks 
beyond the viewable range of the Wii remote, a prompt informed the
user. The only human intervention required during the
experiment was to move the robot back inside the viewable area and resume
the run, and to handle any mechnanical failures that arose. This did not
interrupt the learning process or result in the loss of data.
